% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={BOHEMIA 2024},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{BOHEMIA 2024}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\frame{\titlepage}

\begin{frame}{Problem Statement}
\phantomsection\label{problem-statement}
We will analyze data collected by the Broad One Health Endectocide-based
Malaria Intervention in Africa and examine the efficacy of bed nets as a
means to reduce malaria cases in Kenya and Mozambique.
\end{frame}

\begin{frame}{INTRODUCTION}
\phantomsection\label{introduction}
The Bohemia (Broad One Health Endectocide-based Malaria Intervention in
Africa ) Project is a hub of six leading research institutes with the
plan to administer Ivermectin ( a drug given to humans and livestocks to
prevent parasitic diseases). Although Ivermectin does not kill Malaria
parasites, it attacks mosquitoes when they bite us.
\end{frame}

\begin{frame}{THE PROBLEM}
\phantomsection\label{the-problem}
The world is not on track to achieve the goals proposed by WHO in the
Global Technical Strategy for Malaria 2016-2030 (GTS), and the currently
available tools are unlikely to suffice. 400,000 people still die from
malaria each year making malaria one of the leading causes of child
death. Vector control, the most effective way to fight Malaria is being
challenged by widespread insecticide resistance, and mosquitoes that
avoid insecticides in bednets.
\end{frame}

\begin{frame}{Introduction to Malaria}
\phantomsection\label{introduction-to-malaria}
\textbf{Causes, Symptoms, and High Risk Areas}
\end{frame}

\begin{frame}{Treatments for Malaria}
\phantomsection\label{treatments-for-malaria}
Chloroquine phosphate

ACT
\end{frame}

\begin{frame}{Current Preventative Measures of Malaria}
\phantomsection\label{current-preventative-measures-of-malaria}
\textbf{Bednets} - Bed nets are coated with pyrethroids, an insecticide
that destroys the nervous system of mosquitoes on contact.
\end{frame}

\begin{frame}{Proposed Solution}
\phantomsection\label{proposed-solution}
The five-year Bohemia project funded by Unitaid will conduct a clinical
trial in different ecological and epidemiological settings in east and
southern Africa, specifically Mozambique and Kenya. Ivermectin will be
distributed in mass drug administration campaigns to humans and
livestock in order to reduce mosquito populations that transmit malaria.
\end{frame}

\begin{frame}{Overview of Ivermectin}
\phantomsection\label{overview-of-ivermectin}
\textbf{Structure}

\begin{itemize}
\tightlist
\item
  Semi-synthetic antiparasitic medication derived from avermectins, a
  compound isolated from the Streptomyces avermitilis bacteria .
\end{itemize}
\end{frame}

\begin{frame}{Uses, Limitations, and Misconceptions}
\phantomsection\label{uses-limitations-and-misconceptions}
\end{frame}

\begin{frame}{BOHEMIA Project Goals}
\phantomsection\label{bohemia-project-goals}
\begin{itemize}
\item
  Generate evidence on the impact of ivermectin MDA on malaria infection
  in humans, on mosquito populations, and on the environment, as well as
  on its safety and acceptability by communities.
\item
  Support policy and translation of ivermectin as a potential vector
  control strategy for malaria impact.
\item
  Engage generic drug manufacturers as key partners for malaria
  intervention.
\end{itemize}
\end{frame}

\end{document}
