---
title: "Stopping the Swarm: Bed Nets in Kwale"
author: "Linn Lett Moe, Oysik Saif, Reiner Adakole-Okopi, Samuel Grace Conyers & Solomon Sakakeeny-Smith"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: true
    theme: cerulean
---

```{r, include=FALSE}
# load in libraries
library(reactable)
library(ggbreak)
```

# Introduction

In 2022, 608,000 people died of malaria, of which 95% were in Africa. The best way to reduce malaria related deaths is to prevent transmission through  mosquito bites. The [Broad One Health Endectocide based Malaria Intervention in Africa (BOHEMIA)](https://bohemiaconsortium.org) project concluded a large scale clinical trial to determine if ivermectin, an anti-parasitic drug, is an effective tool to decrease malaria rates within rural communities in Africa, specifically Kenya and Mozambique. Despite interest in new ways to decrease malaria rates, the current most effective way to prevent malaria is the long lasting insecticidal net (LLIN), which is an insecticide treated mesh net that keeps mosquitoes from biting during the night. Using data collected from BOHEMIA’s most recent clinical trial, our goal was to examine bed net usage on an individual and community level, along with its relationship to various factors. This report includes visualizations of our data, in both tabular and graphical formats, along with written descriptions of each visualization.

# Datasets

The code that creates this work can be found [here](https://github.com/sewaneedata/BOHEMIA-2024). We worked with 10 datasets in total. Some of the datasets can be found [here](https://drive.google.com/drive/u/0/folders/1jq1dtoTScgSA9h5vtEtLAtdjp_tF-Nxs), and the remaining datasets are retrieved by the `data.R` script.

1. `kenya_demography.csv` : has demographic information on the sample population.

2. `kenya_safety.csv` : has information on usage of bed nets over 4 visits.

3. `kenya_safety_new.csv`: has information on usage of bed nets for people added in the survey after the initial visit (for kenya_demography).

4. `kenya_efficacy.csv` : has information on the usage of bed nets for children aged 5-15 over 7 visits. And the visits are 2 weeks before kenya_safety visits.

5. `kenya_healthecon_baseline.csv` : has information on the ownership of bed nets.

6. `kenya_healthecon_baseline_new.csv` : has information on the ownership of bed nets for people added in the survey after the initial visit (for kenya_demography)

7. `healthecon_monthly.csv` : has monthly information on the price of bed nets.

8. `malaria_incidence` : has information on malaria incidents over 7 visits for each cluster.

9. `kenya_ae` : has information on the adverse event symptoms.

10. `weather` : has information on the weather data for Mombasa in 2023-2024.

11. `kwale_weather` : has information on the weather data for Kwale in 2023-2024.


# Bed nets

This section uses  the `healthecon_monthly`, `kenya_healthecon`, `kenya_safety`, and `kenya_demography` datasets. Our analysis utilizes data from the following questions, grouped by dataset:

- `healthecon_monthly`
  + What is the cost for each net obtained in Kenyan Shillings?

- `kenya_healthecon`
  + How many bed nets does the household currently own?

- `kenya_safety`
  + Did the subject sleep under a mosquito net last night?
  + In the last week, how many nights did the subject sleep under a bed net?

- `kenya_demography`
  + What is the age of the subject?
  + What is the sex of the subject?


```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
source('question_scripts/1_bednets.R')
```

**Summary of bed net prices (USD)**

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
reactable(bed_net_cost_df, columns=list(), pagination=FALSE)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
print(receive_free_bed_nets)
```

This graph compares the number of households who received nets for free to the number of people who bought nets. There were more households that had to pay for their nets with the study than there were those who got them for free. 

<br /> 
<br />

**Summary of number of bed nets per household**

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
reactable(bed_net_number_df, columns=list(), pagination=FALSE)
```

**Summary of age and sex of people using bed nets in Kwale**


```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
reactable(kenya_safety_summary, columns=list(), pagination=FALSE)
```

This table shows the counts for men and women who slept under a bed net last night, along with the average age of respondents who said yes and no, respectively. Although the sample sizes are slightly different, women were more likely to sleep under a net than men. Additionally, the average age of people who used a net was slightly higher than those who did not.

<br />
<br />

# Ownership, Sufficiency, and Usage

This section uses the `kenya_healthecon`, `kenya_safety`, and `kenya_efficacy` datasets. Our analysis utilizes data from the following questions, grouped by dataset:

- `kenya_healthecon`
  + How many bed nets does the household currently own?

- `kenya_safety`/ `kenya_efficacy`
  + Did the subject sleep under a mosquito net last night?
  + In the last week, how many nights did the subject sleep under a bed net?

**Ownership** : Ownership is whether or not a household own a bed net.

**Sufficiency** : Sufficiency measures if a home has enough bed nets for  the amount of people in the house hold. The standard sufficiency level is 2 people per bed net. 

**Usage** : Usage is whether or not a subject used a bed net last night. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
source('question_scripts/2_correlations.R')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
#Percentage of OSU
perc_osu
```

This layered graph shows the relationship between the two metrics used to measure usage, last night and number of nights over the last week. The similarity between the ratios of yes and no within the last night data set, and seven and zero within the nights over the last week data set, allows for the application of last night usage as an accurate measurement of usage overall. 

<br />
<br />

**Summary of ownership, sufficiency, and usage data**

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
# Table showing Ownership, Sufficiency and Usage Data
reactable(osu_sum, columns=list(), pagination=FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
# created name for graph on ownership, sufficiency, and usage
osu_graph
```

This bar chart shows the percentage values of ownership, sufficiency, and usage within the safety cohort. Ownership represents the percentage of households that own at least one bed net, whereas sufficiency and usage are percentages of the households who own bed nets that have a sufficient amount (2:1 person:net ratio) or that use bed nets, respectively. Out of 85% of the households who own bed nets, 63% are sufficient and 77% use their bed nets. The relationship between sufficiency and usage shows that there are people using bed nets when they don't have sufficient bed nets in their households. This discrepancy could be for one of two reasons. Either there are more than two people sleeping under each bed net or respondents are lying about using bed nets. 

<br />
<br />

# Differences in usage between V1 through V7 within the efficacy cohort

This section uses the `kenya_efficacy` dataset. Our analysis utilizes data from the following questions, grouped by dataset:

- `kenya_efficacy`
  + Did the subject sleep under a mosquito net last night?
  + In the last week, how many nights did the subject sleep under a bed net?

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=FALSE}
source('question_scripts/3_differences.R')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=FALSE}
# Print bar chart of Slept under bed net last night for each visit
differences_usage
```

This bar chart shows changes in usage responses between visits one through seven. Usage is on a steady decline over the course of the trial, until the last visit where there is an increase. But with that being said, the total number of respondents decreases over the course of the trial as well.

<br />
<br />

# Effects of environmental factors on bed net usage

This section uses the `kenya_efficacy`, `kenya_safety`, `kwale_weather`, and `weather` datasets. Our analysis utilizes data from the following questions, grouped by dataset:

- `kenya_safety`/ `kenya_efficacy`
  + Did the subject sleep under a mosquito net last night?

- `weather`/ `kwale_weather`
  + What was the temperature on that day?
  + What was the precipitation on that day?

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/4_effects.R')
weather_new_data
```

This layered graph shows the relationship between two environmental factors, temperature and precipitation, and the usage of bed nets over four months. The usage data is bi-weekly from two different datasets, efficacy and safety where each bar represents the percent usage for each survey. The line shows the change in temperature for each month in celsius while the dotted line shows precipitation in millimeters. This graph shows that there is very little change in percent usage over four months. 

<br />
<br />

```{r, echo=FALSE, message=FALSE, warning=FALSE}
p
```

This layered bar graph shows the relationship between the environmental factors and the usage of bed nets from an efficacy dataset over six months. The line in the graph represents the temperature in celsius for each month, while the dotted line represents the precipitation in millimeters. The usage of bed nets is represented by each bar in a percent usage format. This graph shows that, even though precipitation does not affect the usage of bed nets, temperature has a possible effect on the usage of bed nets as usage increases by almost 15% as temperature decreases by approximately 0.8 degrees celsius between March and April.

<br />
<br />

# Effects of community usage on malaria incidents

This section uses the `kenya_safety` and `mal_incidence` datasets. Our analysis utilizes data from the following questions, grouped by dataset:

- `kenya_efficacy`
  + Did the subject sleep under a mosquito net last night?

- `mal_incidence`
  + How many new malaria incidents have been detected in the cluster?


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/5_communityusage.R')

# Print plot of Bed Net Usage and Malaria Incidence by each visit in safety data
mal_inc_vs_usage
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Print scatter plot of safety data, averaging visits into total % usage
scatter_usage
```

These two graphs both display the relationship between percent usage at a community level and malaria incidence, displayed in two different manners. On both graphs, the x and y axes are percent usage and malaria incidence, respectively, and each point represents a trial cluster. The first graph is faceted by visit and the second graph is colored by villages.

<br />
<br />

# Likelihood of bed net usage

This section uses the `kenya_safety` and `kenya_efficacy` datasets. Our analysis utilizes data from the following questions, grouped by dataset:

- `kenya_safety`/ `kenya_efficacy`
  + Did the subject sleep under a mosquito net last night?

### Safety

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/6_autocorsafe.R')

# Print plot of percentage usage unchanged from previous visits
percent_usage_visits
```

### Efficacy

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/7_autocoreff.R')

# Print plot of percentage usage unchanged from previous visits
autocoreff_usage
```

These two graphs both display the likelihood of each subject sleeping or not sleeping under a bed net in a visit if they slept under a bed net during the last visit of the survey. The bars show the likelihood in a percentage format and the graph is then colored by yes or no.

# Conclusion

65 people are dying each hour from malaria in Africa. To decrease this number, research must be done to inform policy and our work with BOHEMIA is a key step in this process. The next step is for BOHEMIA to publish the results of their clinical trial, which will include our analysis. Then in conjunction with other publications, BOHEMIA’s trial will hopefully be used by the World Health Organization to inform malaria policy in Sub-Saharan Africa.

<br />
<br />

This report is created in partnership with the Sewanee DataLab and the BOHEMIA project.

<img src="https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcRlOe8nXAKTTdh4lrtlEVER4g3Io4C9jcZDOA&s" style="float: right; margin-left: 20px;" alt="Sewanee DataLab" />

<img src="https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcRamh50hTztU9aKFX1GMpFEU1qdjz4OrCnHjg&s" style="float: left; margin-right: 20px;" alt="The BOHEMIA project" />
