---
title: "Stopping the Swarm: Bed Nets in Kwale"
author: "Linn Lett Moe, Oysik Saif, Reiner Adakole-Okopi, Samuel Grace Conyers & Solomon Sakakeeny-Smith"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: true
    theme: cerulean
---

```{r, include=FALSE}
# load in libraries
library(reactable)
library(ggbreak)
```

# Introduction
- give our problem statement
- state our goals for the report
- introduce bed nets, more specfically LLINs and define issues
- mention BOHEMIA's interest in bed nets as a way to prevent childhood malaria 

# Bed Nets
```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
source('question_scripts/1_bednets.R')
```

## Summary of Bed Net Prices
```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
reactable(bed_net_cost_df, columns=list(), pagination=FALSE)
```

## Graph of Free Bed Nets vs Not Free Bed Nets

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
print(receive_free_bed_nets)
```

This graph compares the number of households who received nets for free to the number of nets who bought nets. There were more households that had to pay for their nets with the study than there were those who got them for free. 

## Summary of Number of Bed Nets per Household

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
reactable(bed_net_number_df, columns=list(), pagination=FALSE)
```

## Summary of Age and Sex of People Using Bed Nets in Kwale
***This table shows the counts for men and women who slept under a bed net last night, along with the average age of respondents who said yes and no, respectively. Although the sample sizes are slightly different, women were more likely to sleep under a net than men. Additionally, the average age of people who used a net was slightly higher than those who did not.


```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
reactable(kenya_safety_summary, columns=list(), pagination=FALSE)
```

This table shows the counts for men and women who slept under a bed net last night, along with the average age of respondents who said yes and no, respectively. Although the sample sizes are slightly different, women were more likely to sleep under a net than men. Additionally, the average age of people who used a net was slightly higher than those who did not.

# Ownership, Sufficiency, and Usage
Within this section, we will have subsections going over each portion of our analysis:

## Relationship between ownership, sufficiency, and usage

- household data for each attribute over three months 
- bar graphs for visit V1 through V4 with all three attributes
- tabulate data for each attribute in five number summary

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
```



## Differences in usage between V1 through V7 within the efficacy cohort

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=FALSE}
```
This bar chart shows changes in usage responses between visits one through seven. Usage is on a steady decline over the course of the trial, until the last visit where there is an increase. But with that being said, the total number of respondents decreases over the course of the trial as well. 
```{r}

```

This layered graph shows the relationship between the two metrics used to measure usage, last night and number of nights over the last week. The similarity between the ratios of yes and no within the last night data set, and seven and zero within the nights over the last week data set, allows for the application of last night usage as an accurate measurement of usage overall.

## Effects of environmental factors on bed net usage

```{r, echo=FALSE, message=FALSE, warning=FALSE}
```


## Effects of community usage on malaria incidence 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/5_communityusage.R')

# Print plot of Bed Net Usage and Malaria Incidence by each visit in safety data
mal_inc_vs_usage
```

write some words then print another graph

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Print scatter plot of safety data, averaging visits into total % usage
scatter_usage
```


## Possible auto correlations
### Safety

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/6_autocorsafe.R')

# Print plot of percentage usage unchanged from previous visits
percent_usage_visits
```

### Efficacy

```{r, echo=FALSE, message=FALSE, warning=FALSE}
```

