---
title: "Stopping the Swarm: Bed Nets in Kwale"
author: "Reiner, Oysik, Solomon, Sam & Linn (add full names in alphabetical order)"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: true
    theme: cerulean
---

```{r, include=FALSE}
# load in libraries
library(reactable)
library(ggbreak)
```

# Introduction
- give our problem statement
- state our goals for the report
- introduce bed nets, more specfically LLINs and define issues
- mention BOHEMIA's interest in bed nets as a way to prevent childhood malaria 

# Bed Nets
```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
source('question_scripts/1_bednets.R')

# printing bednet table
reactable(kenya_safety_summary, columns=list(), pagination=FALSE)

# print the receive free bed nets graph
receive_free_bed_nets
```

# Ownership, Sufficiency, and Usage
Within this section, we will have subsections going over each portion of our analysis:

## Relationship between ownership, sufficiency, and usage

- household data for each attribute over three months 
- bar graphs for visit V1 through V4 with all three attributes
- tabulate data for each attribute in five number summary

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
source('question_scripts/2_correlations.R')
```



## Differences in usage between V1 through V7 within the efficacy cohort

```{r, echo=FALSE, message=FALSE, warning=FALSE, comment=FALSE}
source('question_scripts/3_differences.R')
```


## Effects of environmental factors on bed net usage

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#source('question_scripts/4_effects.R')
```


## Effects of community usage on malaria incidence 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/5_communityusage.R')
```

## Possible auto correlations
### Safety

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/6_autocorsafe.R')
```

### Efficacy

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/7_autocoreff.R')
```

