---
title: "Project proposal"
author: "Reiner, Oysik, Solomon, Sam & Linn"
date: "2024-07-01"
output: html_document
---
# Introduction
- give our problem statement
- state our goals for the report
- introduce bed nets, more specfically LLINs and define issues
- mention BOHEMIA's interest in bed nets as a way to prevent childhood malaria 

# Bed Nets
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/1_bednets.R')
```
# Ownership, Sufficiency, and Usage
Within this section, we will have subsections going over each portion of our analysis:

## Relationship between ownership, sufficiency, and usage

- household data for each attribute over three months 
- bar graphs for visit V1 through V4 with all three attributes
- tabulate data for each attribute in five number summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/2_correlations.R')
```



## Differences in usage between V1 through V7 within the efficacy cohort

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/3_differences.R')
```


## Effects of environmental factors on bed net usage

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/4_effects.R')
```


## Effects of community usage on malaria incidence 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/5_communityusage.R')
```

## Possible auto correlations
### Safety

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/6_autocorsafe.R')
```

### Efficacy

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('question_scripts/7_autocoreff.R')
```

